Meta-analysis

### 2020-07-01 04_MetaAnalysis.Rmd
insert formula for Standardised mean differences
one line addition
Changed the response to response ratio, or mean difference for easier interpretation of the results

@@

Let's simplify our data by removing the control data, converting disease pressure (`D_pres`) to a factor and selecting only the columns of data necessary for analysis.

```{r metafor_organisation}
dat1 <-
   slimmer_PM_dat %>%
   filter(fungicide_ai != "control") %>% #remove controls from the data
   mutate(spray_management =
             factor(
                spray_management,
                c(
                   "Early",
                   "Recommended",
                   "Recommended_plus",
                   "Late",
                   "Late_plus"
                )
             ),
          D_pres = 
             factor(D_pres,
                    c("lowD",
                      "highD"))) %>%
   select(
      trial,
      trial_ref,
      location,
      year,
      row_spacing,
      host_genotype ,
      spray_management,
      fungicide_ai,
      D_pres,
      grain_yield.t.ha,
      grain_SMD,
      dose,
      vi,
      vi2
      )
```

@@

```{r}
hist_usq(dat1$grain_yield.t.ha)
hist_usq(log(dat1$grain_yield.t.ha))
hist_usq(sqrt(dat1$grain_yield.t.ha))
hist_usq(dat1$grain_SMD)
```

@@

```{r Metafor-analysis}
PM_mv <- rma.mv(
   yi = grain_SMD,
   vi,
   mods = ~ spray_management - 1,
   method = "ML",
   random = ~ spray_management | trial,
   struct = "UN",
   data = dat1
)
summary(PM_mv)
```

@@

```{r rma_noRandomInteractiveTerm}
PM_mv_St <- rma.mv(
   yi = grain_SMD,
   vi,
   mods = ~ spray_management,
   method = "ML",
   random = list( ~ 1 | trial),
   data = dat1
)

PM_mv_St1 <- rma.mv(
   yi = grain_SMD,
   vi,
   mods = ~ spray_management,
   method = "ML",
   random = list(
      ~ 1 |
         location / year / trial_ref / dose / host_genotype / factor(row_spacing) /
         spray_management
   ),
   data = dat1
)

@@

```{r metafor_plot}
efficacy %>%
   mutate(Treatment = factor(Treatment, levels = rev(
      c(
         "Early",
         "Recommended",
         "Recommended_plus",
         "Late",
         "Late_plus"
      )
   ))) %>%
   ggplot(aes(Treatment, Mean)) +
   geom_hline(
      yintercept = seq(-0.4, 1.8, by = 0.2),
      color = usq_cols("usq charcoal"),
      linetype = 3
   ) +
   geom_hline(yintercept = 0) +
   geom_point(aes(size = 1 / SE), shape = 15) +
   geom_linerange(aes(ymin = CIs_lower, ymax = CI_upper)) +
   coord_flip()
```

@@

We will add the intercept back into this model for ease of interpretation. 
```{r D_pres-Meta}
PM_mv_Dp <- rma.mv(
   yi = grain_SMD,
   vi,
   mods = ~ spray_management *D_pres,
   method = "ML",
   random = ~ spray_management | trial,
   struct = "UN",
   data = dat1
)

>>>>

To visualise this formula in mathematical notation:  
$SMD = \frac{Y_i-\overline{Y_c}}{\sigma_p}$

@@

Let's simplify our data by removing the control data, converting disease pressure (`D_pres`) to a factor and selecting only the columns of data necessary for analysis.
We will also include the mean difference or response ratio `grain_MD`, between the treatment and control as a comparison of responses.

```{r metafor_organisation}
dat1 <-
   slimmer_PM_dat %>%
   filter(fungicide_ai != "control") %>% #remove controls from the data
   mutate(spray_management =
             factor(
                spray_management,
                c(
                   "Early",
                   "Recommended",
                   "Recommended_plus",
                   "Late",
                   "Late_plus"
                )
             ),
          D_pres = 
             factor(D_pres,
                    c("lowD",
                      "highD")),
          grain_MD = grain_yield.t.ha - yi_C) %>%
   select(
      trial,
      trial_ref,
      location,
      year,
      row_spacing,
      host_genotype ,
      spray_management,
      fungicide_ai,
      D_pres,
      grain_yield.t.ha,
      grain_SMD,
      grain_MD,
      dose,
      vi,
      vi2
      )
```

@@

```{r}
hist_usq(dat1$grain_yield.t.ha)
hist_usq(log(dat1$grain_yield.t.ha))
hist_usq(sqrt(dat1$grain_yield.t.ha))
hist_usq(dat1$grain_MD)
```

@@

```{r Metafor-analysis}
PM_mv <- rma.mv(
   yi = grain_MD,
   vi,
   mods = ~ spray_management - 1,
   method = "ML",
   random = ~ spray_management | trial,
   struct = "UN",
   data = dat1
)
summary(PM_mv)
```

@@

```{r rma_noRandomInteractiveTerm}
PM_mv_St <- rma.mv(
   yi = grain_MD,
   vi,
   mods = ~ spray_management,
   method = "ML",
   random = list( ~ 1 | trial),
   data = dat1
)

PM_mv_St1 <- rma.mv(
   yi = grain_MD,
   vi,
   mods = ~ spray_management,
   method = "ML",
   random = list(
      ~ 1 |
         location / year / trial_ref / dose / host_genotype / factor(row_spacing) /
         spray_management
   ),
   data = dat1
)

@@

```{r metafor_plot}
efficacy %>%
   mutate(Treatment = factor(Treatment, levels = rev(
      c(
         "Early",
         "Recommended",
         "Recommended_plus",
         "Late",
         "Late_plus"
      )
   ))) %>%
   ggplot(aes(Treatment, Mean)) +
   geom_hline(
      yintercept = seq(-0.05, 0.3, by = 0.05),
      color = usq_cols("usq charcoal"),
      linetype = 3
   ) +
   geom_hline(yintercept = 0) +
   geom_point(aes(size = 1 / SE), shape = 15) +
   geom_linerange(aes(ymin = CIs_lower, ymax = CI_upper)) +
   coord_flip()
```

@@

We will add the intercept back into this model for ease of interpretation. 
```{r D_pres-Meta}
PM_mv_Dp <- rma.mv(
   yi = grain_MD,
   vi,
   mods = ~ spray_management * D_pres - 1,
   method = "ML",
   random = ~ spray_management | trial,
   struct = "UN",
   data = dat1
)
